### 2017-03-27 conclusion.tex
Added final thoughts.

In Chapter 2, we presented a detailed description of the new superbubble model,
implemented in the SPH code {\sc Gasoline2}.  We rely on the strongly
self-limiting process of thermal evaporation \citep{Cowie1977}, where cold mass
is evaporated into a hot bubble at a rate strongly dependent on the temperature
of the hot bubble. This drives the interior of the bubble to a temperature of a
few $10^6$ K, evaporating material more or less rapidly as the temperature dips
above or below this value.  This is the characteristic temperature for SN-heated
gas.  We use this physics to develop a new model for SN feedback, that gives
realistic estimates for cooling in unresolved hot bubbles, and accurately
calculates the mass loading of SN energy.  We demonstrated that this model is
insensitive to resolution, unresolved ISM structure, and uncertain (turbulent)
magnetic fields.  The strong temperature dependence of thermal evaporation means
that significant changes to the conduction rate (such as the supression by
magnetic fields) result in only slight changes to the temperature of
feedback-heated gas.  Finally, after investigating the behaviour of individual
bubbles, we showed that superbubble feedback is more effective at both
regulating star formation and at driving galactic winds.

@@

It has been suggested by numerous studies \citep{Benson2003,Bower2006} that AGN
feedback is critical to shaping the galaxy luminosity function.  Most
observations \citep{Kauffmann2003b} show that strong AGN are hosted in galaxies
with halo masses slightly greater than $\sim10^{12}\;M_\odot$.  By simulating a
collection of galaxies that bracket this mass, but omitting the effects of AGN
feedback, we were able to show that SN alone break down as a mechanism of
regulating star formation in these massive galaxies.  Importantly, this also
results in large angular momentum losses for gas within the disc, funneling
material to the central regions where SMBHs reside.  This, combined with the
failure of SN-driven galactic winds, suggests that SN are actually the mechanism
that determines where powerful AGN occur, a mechanism that has begun to be studied in
\citet{Bower2016}.  Uncertainties in the unresolved ISM are unlikely to
significantly change the characteristic mass that ``needs'' AGN for regulation.
As we showed in Chapter 2, the strongly self-limiting nature of thermal
conduction makes the temperature of feedback-heated gas insensitve to unresolved
structure in both gas density and magnetic fields.

@@

\section{Final Thoughts}
\bibliographystyle{mnras}
\bibliography{library}

>>>>

In Chapter 2, we presented a detailed description of the new superbubble model,
implemented in the SPH code {\sc Gasoline2}.  We rely on the strongly
self-limiting process of thermal evaporation \citep{Cowie1977}, where cold mass
is evaporated into a hot bubble at a rate strongly dependent on the temperature
of the hot bubble. This drives the interior of the bubble to a temperature of a
few $10^6$ K, evaporating material more or less rapidly as the temperature dips
above or below this value.  This is the characteristic temperature for SN-heated
gas.  We use this physics to develop a new model for SN feedback, that gives
realistic estimates for cooling in unresolved hot bubbles, and accurately
calculates the mass loading of SN energy.  We demonstrated that this model is
insensitive to resolution, unresolved ISM structure, and uncertain (turbulent)
magnetic fields.  The strong temperature dependence of thermal evaporation means
that significant changes to the conduction rate (such as the suppression by
magnetic fields) result in only slight changes to the temperature of
feedback-heated gas.  Finally, after investigating the behaviour of individual
bubbles, we showed that superbubble feedback is more effective at both
regulating star formation and at driving galactic winds.

@@

It has been suggested by numerous studies \citep{Benson2003,Bower2006} that AGN
feedback is critical to shaping the galaxy luminosity function.  Most
observations \citep{Kauffmann2003b} show that strong AGN are hosted in galaxies
with halo masses slightly greater than $\sim10^{12}\;M_\odot$.  By simulating a
collection of galaxies that bracket this mass, but omitting the effects of AGN
feedback, we were able to show that SN alone break down as a mechanism of
regulating star formation in these massive galaxies.  Importantly, this also
results in large angular momentum losses for gas within the disc, funneling
material to the central regions where SMBHs reside.  This, combined with the
failure of SN-driven galactic winds, suggests that SN are actually the mechanism
that determines where powerful AGN occur, a mechanism that has begun to be studied in
\citet{Bower2016}.  Uncertainties in the unresolved ISM are unlikely to
significantly change the characteristic mass that ``needs'' AGN for regulation.
As we showed in Chapter 2, the strongly self-limiting nature of thermal
conduction makes the temperature of feedback-heated gas insensitive to unresolved
structure in both gas density and magnetic fields.

@@

\section{Final Thoughts}
Less than a century ago, the most fundamental nature of galaxies was
contentious.  Prominent astronomers argued ``spiral nebulae'' were members of
our own galaxy, the Milky Way.  Today, we stand on the shoulders of legion
observers, theorists, and simulators in constructing a theory of galaxy
formation.  While these past generations have painted a picture of galaxy
formation ultimately as gravitational collapse through hierarchical, bottom-up
merging, many details remain unclear.  Perhaps the most puzzling \& important
question is the inefficiency of star formation at all scales.  At best, a galaxy
may convert a third of it's baryons into stars, with most galaxies forming stars
even more ineffectively.  This thesis has explored one mechanism for this
inefficiency, feedback by supernovae.  We have shown that thermal conduction
is critical to evaporating the star-forming ISM into the hot outflows that starve
young, high-redshift galaxies of star formation fuel.  This mechanism is effective
in galaxies up to the mass of our own: it breaks down in more massive galaxies.
This tells us two important facts about how galaxies regulate their star
formation.  First, it tells us that supernovae are the only source of energy
needed to regulate star formation in low to medium size galaxies.  Second, it
tells us that supernovae {\it cannot} be the only source of energy that
regulates the formation of massive galaxies.  While many questions remain about
the processes that govern the life cycle of galaxies, the results shown here
provide a solid foundation for understanding one of the most important processes:
how supernovae regulate galaxy formation.

\bibliographystyle{mnras}
\bibliography{library}
